\documentclass[10pt, letterpaper]{article}
\usepackage[top=0.5in, bottom=0.5in, left=0.7in, right=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{array}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Decorative section header with rules on both sides
\newcommand{\ressection}[1]{%
  \vspace{6pt}
  \begin{center}
    \rule{0.3\textwidth}{0.4pt}\quad\textbf{#1}\quad\rule{0.3\textwidth}{0.4pt}
  \end{center}
  \vspace{2pt}
}

% Centered experience entry
\newcommand{\expentry}[3]{%
  \begin{center}
    \textbf{#1} \textbar{} #2 \textbar{} #3
  \end{center}
}

\begin{document}

% ---- Header ----
\begin{center}
  {\fontsize{26}{30}\selectfont\textsc{\MakeUppercase{Alok Patel}}}\\[5pt]
  alokothro@gmail.com \quad\textbar\quad (803) 899-4393 \quad\textbar\quad Rock Hill, SC 29730 \quad\textbar\quad \textbf{WWW:} https://github.com/Alokothro
\end{center}

% ---- Summary ----
\ressection{Summary}

\noindent Student at the University of South Carolina, majoring in computer science, with a strong passion to dive into the field. A dedicated student who consistently meets deadlines and is eager to explore different areas of computer science to gain insight from every angle and achieve mastery.

% ---- Skills ----
\ressection{Skills}

\vspace{2pt}
\begin{tabularx}{\textwidth}{X X}
  \begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=0pt]
    \item Python
    \item Java
    \item HTML
    \item C++
  \end{itemize}
  &
  \begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=0pt]
    \item Organization
    \item Creativity
    \item Communications
    \item Critical Thinking
  \end{itemize}
\end{tabularx}

% ---- Experience ----
\ressection{Experience}

\expentry{Manager}{AMR Services - Rock Hill, SC}{05/2024 - Current}

\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=1pt]
  \item Developed and maintained Excel-based financial tracking sheets to manage profits, expenses, and revenue, gaining experience in data analysis and financial modeling.
  \item Designed and implemented a payroll system using spreadsheet formulas to calculate employee compensation based on job attendance and profit sharing, reinforcing logic and problem-solving skills.
  \item Integrated Calendly for customer appointment bookings, streamlining client scheduling and improving service efficiency.
  \item Designed marketing materials (door hangers) to attract new clients, enhancing creativity and user engagement in promotional strategies.
  \item Managed all aspects of business operations, including customer relations, team coordination, and financial management.
\end{itemize}

\vspace{4pt}

\expentry{Associate}{The Home Depot - Rock Hill, SC}{06/2022 - Current}

\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=1pt]
  \item Developed strong problem-solving skills by assisting customers with various inquiries and troubleshooting order issues.
  \item Collaborated with other associates to optimize order fulfillment processes and efficiently fill orders.
  \item Gained hands-on experience with inventory management systems and data entry, reinforcing attention to detail and organizing orders.
\end{itemize}

% ---- Education and Training ----
\ressection{Education and Training}

\begin{center}
  University of South Carolina - Columbia \quad\textbar\quad Columbia, SC\\[3pt]
  Computer Science\\[5pt]
  \textbf{Relevant Coursework}
\end{center}

\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=1pt]
  \item Algorithmic Design 1 \& 2
  \item Software Engineering
  \item Advance Programming Techniques
\end{itemize}

\begin{center}
  \textbf{Projects}
\end{center}

\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=1pt]
  \item Developed a temporary clock-in system for hotel employees to track working hours and attendance which was written in Python due to their system being down
  \item Made a basic car infotainment system interface, providing features such as media control, navigation display, music, and basic vehicle information
\end{itemize}

\vspace{4pt}

\begin{center}
  Rock Hill High School \quad\textbar\quad Rock Hill, SC\\[3pt]
  2019--2023\\
  \textbf{High School Diploma}
\end{center}

\end{document}
