\documentclass[10.5pt, letterpaper]{article}
\usepackage[top=0.5in, bottom=0.5in, left=0.65in, right=0.65in]{geometry}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section header command
\newcommand{\ressection}[1]{%
  \vspace{6pt}
  \noindent\textbf{#1}
  \vspace{1pt}
  \hrule
  \vspace{4pt}
}

\begin{document}

% ---- Header ----
\begin{center}
  {\large\textbf{Alok Patel}}\\[2pt]
  Rock Hill, SC \textbar{} alokothro@gmail.com \textbar{} (803) 899 -- 4393 \textbar{} github.com/Alokothro
\end{center}

\vspace{4pt}
\hrule
\vspace{4pt}

% ---- Education ----
\ressection{EDUCATION}

\noindent\textbf{University of South Carolina} \hfill \textbf{Columbia, SC}\\
\textit{Bachelor of Science in Computer Science} \hfill \textit{May 2027}

\vspace{8pt}

% ---- Work Experience ----
\ressection{WORK EXPERIENCE}

\noindent\textbf{Manager} - \textit{AMR Services} \textbar{} Rock Hill, SC \textbar{} May 2024 -- Present
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=2pt]
  \item Integrated Calendly API for automated scheduling, increasing appointment volume by 25\%.
  \item Developed and maintained Excel-based financial tracking sheets to manage profits, expenses, and revenue, using data analysis and financial modeling.
  \item Designed and implemented a payroll system using spreadsheet formulas to calculate employee compensation based on job attendance and profit sharing, reinforcing logic and problem-solving skills.
\end{itemize}

\vspace{4pt}
\noindent\textbf{Associate} -- \textit{The Home Depot} \textbar{} Rock Hill, SC \textbar{} Jun 2022 -- Present
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=2pt]
  \item Provided technical and product support to 200+ customers daily, applying problem-solving skills and customer service best practices.
  \item Collaborated in cross-functional teams to fulfill online and in-store orders, ensuring timely delivery and stock accuracy.
  \item Utilized inventory management software to track SKUs and resolve logistical discrepancies with 95\% accuracy.
\end{itemize}

\vspace{4pt}

% ---- Projects & Leadership ----
\ressection{PROJECTS \& LEADERSHIP EXPERIENCE}

\noindent\textbf{Hotel Employee Clock-in System} -- \textit{Python}
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=2pt]
  \item Developed a GUI-based time-tracking system to replace a downed clock-in system for hotel staff.
  \item Implemented real-time attendance logging, file-based storage, and user input validation.
  \item Improved system availability during outages and enhanced data accuracy.
\end{itemize}

\vspace{4pt}
\noindent\textbf{Vehicle Infotainment UI Prototype} -- \textit{Java}
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=2pt]
  \item Created an interactive mock-up of an automotive infotainment system with modules for media playback, navigation, and system info.
  \item Emulated real-world user interface flow and modular code structure for future expandability.
  \item Applied principles of human-computer interaction and event-driven programming.
\end{itemize}

\vspace{4pt}
\noindent\textbf{Alumni Relations Director} -- \textit{Phi Iota Alpha} \textbar{} University of South Carolina \textbar{} May 2024 -- May 2025
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=2pt]
  \item Designed and maintained alumni contact database using Google Sheets and automation tools, improving outreach capacity.
  \item Coordinated email campaigns and digital updates, increasing engagement with events and chapter news for 100+ alumni.
  \item Led technical setup for hybrid events (Zoom), enhancing accessibility and communications.
\end{itemize}

\vspace{4pt}

% ---- Skills & Competencies ----
\ressection{SKILLS \& COMPETENCIES}

\begin{tabularx}{\textwidth}{X X}
  \begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=0pt]
    \item \textbf{National Certifications:} Microsoft Excel, PowerPoint, and Word - 2023
    \item \textbf{Languages:} Python, Java, C++, JavaScript, and HTML
    \item \textbf{Frameworks \& Tools:} Flask, SQLite, Git, GitHub, Visual Studio Code, Excel (Advanced), MARS (MIPS)
  \end{itemize}
  &
  \begin{itemize}[leftmargin=1.5em, itemsep=4pt, topsep=0pt]
    \item \textbf{Enrichment:} Learning Python scripting, Git/GitHub, automation, and troubleshooting. Includes a capstone project involving real-world IT automation scenarios using Python and version control tools. - 08/01/2025
    \item \textbf{Core Concepts:} Object-Oriented Programming, Data Structures \& Algorithms, Time \& Space Complexity, Recursion, Debugging, RESTful API Design, and Unit Testing
    \item \textbf{Development Practices:} Scrum Methodology, Code Reviews, CI/CD (GitHub Actions), Documentation, Project Planning, and Team Collaboration
  \end{itemize}
\end{tabularx}

\end{document}
