\documentclass[11pt, letterpaper]{article}
\usepackage[top=0.75in, bottom=0.75in, left=1in, right=1in]{geometry}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\begin{document}

% ---- Header ----
\begin{minipage}[t]{0.55\textwidth}
  {\fontsize{26}{30}\selectfont Alok \hspace{4pt} Patel}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
  \raggedleft
  Rock Hill, Sc 29730\\
  803-899-4393\\
  alokothro@gmail.com
\end{minipage}

\vspace{6pt}
\hrule
\vspace{4pt}

% ---- Professional Summary ----
\textbf{\large Professional Summary}\\[4pt]
Hardworking learner that stays on top of fast-paced performance demands and upholds the highest
standard for his work. Resourceful problem-solver with excellent communication that consistently
produces quality work. I am a quick learner with excellent problem-solving skills and a passion for
staying up-to-date with the latest industry trends and technologies.

\vspace{4pt}
\hrule
\vspace{4pt}

% ---- Skills ----
\textbf{\large Skills}\\[4pt]
\begin{tabularx}{\textwidth}{X X X X X}
  Python & Java & Marketing & Stocks & Crypto
\end{tabularx}

\vspace{4pt}
\hrule
\vspace{4pt}

% ---- Experience ----
\textbf{\large Experience}

\vspace{4pt}
June 2022 -- August 2023\\
The Home Depot - Rock Hill, Sc\\
Associate
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=2pt]
  \item Helped customers navigate stores, complete sales, and satisfied customers' questions.
  \item Worked with team members to accomplish tasks and meet targets.
  \item Developed and maintained high levels of knowledge of company products, promotions and store sales functions.
  \item Greeted customers and asked questions to assess needs.
  \item Coordinated with loss and prevention officers to track misplaced and damaged items.
  \item Recommended merchandise to suit customer budget and preferences.
\end{itemize}

\vspace{6pt}
May 2020 -- June 2023\\
Self Employed - Rock Hill, Sc\\
Landscaper
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=2pt]
  \item Kept lawns attractive and healthy with regular mowing and watering.
  \item Improved shape and growth of trees, shrubs and flowers with trimming.
  \item Planted flower beds and laid mulch in attractive designs with good drainage.
  \item Prepared planting areas and planted trees, shrubs and other flora.
  \item Improved yard and garden appearance with decorative stones and ornaments.
  \item Planned landscaping designs from customer desires, budget and local climate.
\end{itemize}

\vspace{4pt}
\hrule
\vspace{4pt}

% ---- Education ----
\textbf{\large Education}

\vspace{4pt}
2019--2023\\
Rock Hill High School\\
\begin{tabularx}{\textwidth}{X X X}
  Graduated with 4.3 GPA (weighted) & Graduated with Honors & Obtained the Life Scholarship
\end{tabularx}

\vspace{4pt}
2023--Present\\
University of South Carolina\\
College (Major: Computer Science)

\vspace{4pt}
\hrule
\vspace{4pt}

% ---- Language ----
\textbf{\large Language}

\vspace{4pt}
\begin{tabularx}{\textwidth}{X X X}
  Gujarati & English & Hindi \\[6pt]
  Fluent   & Native  & Intermediate
\end{tabularx}

\end{document}
